\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{enumerate} % Import the enumerate package
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{float}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{verbatim}


% Listings settings for Python code
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    stringstyle=\color{red},
    commentstyle=\color{green!70!black},
    numberstyle=\tiny\color{gray},
    numbers=left,
    stepnumber=1,
    numbersep=8pt,
    showspaces=false,
    showstringspaces=false,
    frame=single,
    breaklines=true,
    breakatwhitespace=true,
    tabsize=4,
    captionpos=b
}

% Define vibrant colors for white background
\definecolor{numb}{rgb}{0, 0.5, 1}       % Bright blue for numbers
\definecolor{punct}{rgb}{0.5, 0.5, 0.5}  % Medium gray for punctuation
\definecolor{delim}{rgb}{0.8, 0.1, 0.1}  % Bright red for delimiters

\lstdefinelanguage{json}{
    basicstyle=\normalfont\ttfamily,
    numbers=left,
    numberstyle=\scriptsize,
    stepnumber=1,
    numbersep=8pt,
    showstringspaces=false,
    breaklines=true,
    frame=lines,
    literate=
	    *{0}{{{\color{numb}0}}}{1}
	    {1}{{{\color{numb}1}}}{1}
	    {2}{{{\color{numb}2}}}{1}
	    {3}{{{\color{numb}3}}}{1}
	    {4}{{{\color{numb}4}}}{1}
	    {5}{{{\color{numb}5}}}{1}
	    {6}{{{\color{numb}6}}}{1}
	    {7}{{{\color{numb}7}}}{1}
	    {8}{{{\color{numb}8}}}{1}
	    {9}{{{\color{numb}9}}}{1}
	    {:}{{{\color{punct}{:}}}}{1}
	    {,}{{{\color{punct}{,}}}}{1}
	    {\{}{{{\color{delim}{\{}}}}{1}
	    {\}}{{{\color{delim}{\}}}}}{1}
	    {[}{{{\color{delim}{[}}}}{1}
	    {]}{{{\color{delim}{]}}}}{1}
	    {true}{{{\color{numb}{true}}}}{1}
	    {false}{{{\color{numb}{false}}}}{1},
}


\title{Emergency Response: A Multi-Agent System}
\author{Sheena Maria Lang, Antonio Lobo Santos, Zachary Parent, \\ María del Carmen Ramírez Trujillo and Bruno Sánchez Gómez}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Introduction}
This report presents the final implementation and results of our multi-agent system (MAS) for emergency response coordination. Building upon our previous designs from Tasks 1 and 2, we have developed a complete, functional system that demonstrates the effectiveness of agent-based approaches in managing complex emergency scenarios.

The system is implemented using CrewAI \cite{crewai}, a framework that enables the creation and coordination of specialized agent crews. Each crew is designed with specific responsibilities and operates through well-defined processes, ensuring efficient handling of emergency situations. The implementation includes:

\begin{itemize}
    \item \textbf{Emergency Services Crew:} Handles initial emergency assessment and coordination
    \item \textbf{Firefighter Agent Crew:} Manages firefighting resources and operations
    \item \textbf{Medical Services Crew:} Coordinates medical response and hospital resources
    \item \textbf{Public Communication Crew:} Manages public information and communication
\end{itemize}

\paragraph{Report Structure:}
\begin{itemize}
    \item Section \ref{sec:crew_design} details the design and implementation of each crew, including their process definitions, data models and tools
    \item Section \ref{sec:crew_interaction} explains the interaction mechanisms between crews and the overall system flow
    \item Section \ref{sec:testing} presents the design and results of system testing and validation
    \item Section \ref{sec:conclusion} concludes with insights and potential future improvements
\end{itemize}

The implementation builds upon our previous design while introducing several refinements based on practical considerations and testing results. These modifications are documented and justified throughout the report. The complete source code, along with setup instructions and required input files, is provided in the accompanying project repository.

\input{sections/design/design_overview}

\input{sections/design_principles}

\input{sections/design/tools}

\subsection{Emergency Services Crew}
\input{sections/design/emergency_services}
\input{sections/implementation/emergency_services}

\subsection{Firefighter Agent Crew}
\input{sections/design/firefighters}
\input{sections/implementation/firefighters}

\subsection{Medical Services Crew}
\input{sections/design/medical_services}
\input{sections/implementation/medical_services}

\subsection{Public Communication Crew}
\input{sections/design/public_communications}
\input{sections/implementation/public_communications}

\input{sections/crew_interaction}

\input{sections/testing/testing}

\section{Conclusion}
\label{sec:conclusion}

\paragraph{System Overview}
This report showcased the implementation and testing of a multi-agent system (MAS) for coordinating emergency responses. 
Using the CrewAI framework \cite{crewai}, we built a system with specialized agent crews (emergency services, firefighting, medical responses, and public communication), that work together to handle complex scenarios efficiently.

\paragraph{Testing and Results}
Testing showed the system's ability to manage diverse emergencies with strong collaboration between crews, demonstrating both its adaptability and potential. Specifically, two possible test cases were simulated to evaluate the performance of the system under different emergency scenarios. The first involved a fire with injured individuals requiring both medical and firefighting responses, while the second simulated a large-scale fire without injuries. In both cases, the transcripts used to simulate these scenarios successfully triggered the appropriate workflows, with each agent crew performing its tasks as designed. The system effectively coordinated between teams, processed the inputs correctly, and generated detailed reports, confirming that the workflows function as expected in handling diverse emergencies.

\paragraph{Future Work}
All in all, we consider that the work presented constitutes a strong foundational framework for developing a real-world tool to assist in managing emergency situations; nevertheless, it represents only an initial effort, with several areas requiring further refinement and improvement before it can be deployed in practical scenarios. We will now outline several points for future work.

Firstly, regarding the inconsistency in the timestamps due to the agents' inability to access a centralized clock, a custom tool could be developed to provide synchronized timestamps across all agents. This would resolve the issue and ensure accurate temporal coordination, which is essential for real-world deployment where precise timing is critical.

Deploying a voice-to-text transcription tool would greatly improve the system's real-world applicability. Such a tool could transcribe emergency voice calls into structured text, allowing agents to process emergency details more efficiently and reducing reliance on pre-structured inputs. Additionally, a complementary tool to translate street names or neighborhood descriptions into precise coordinates, while retaining the original address, would address the practical reality that emergency callers are unlikely to provide exact coordinates. This enhancement would make the system more practical and user-friendly in real-world scenarios. It could also solve the limitation of placeholder text in the Public Communication Report, as the information regarding the neighborhood or streets could be extracted from the transcript, as it is likely to be something provided by the caller. Nevertheless, integrating the system with a geolocation service to translate coordinates into meaningful place names would be another way of retrieving that information in case it gets lost in the workflow. This last improvement could be really demanding and beyond the scope of the project's objectives.

\paragraph{Summary}
By addressing these limitations and implementing these proposed improvements, the system can evolve into a more robust, practical, and reliable tool for real-world emergency response scenarios.
Overall, this work lays a solid foundation for building smarter emergency response tools. While it's just the beginning, it's clear that agent-based systems have huge potential in this field. With continued development, testing, and collaboration, this system could evolve into a truly powerful tool for managing emergencies in real-world situations.

\section{References}
\bibliography{references}
\bibliographystyle{plain}
\end{document}
