\documentclass{beamer}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{float}
\usepackage{fontawesome}
\usepackage{multicol}
\usepackage{listings}

\lstset{
    language=Python,
    basicstyle=\ttfamily\footnotesize,
    breaklines=true,
    frame=single,
    numbers=none,
    keywordstyle=\color{red}\bfseries,
    stringstyle=\color{green!60!black},
    commentstyle=\color{gray},
    showstringspaces=false,
    columns=flexible,
    backgroundcolor=\color{gray!10},
}

% Beamer theme settings
\usetheme{CambridgeUS}
\usecolortheme{default}

\title{Collaborative System Coordination Design for Urban Crisis: Resolution Using Multi-Agent Technology}
\author{Team 05}
\date{\today}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

% Introduction
\section{Introduction}
\begin{frame}{Introduction}
    \begin{itemize}
        \item \textbf{Objective}: Design the cooperation and coordination mechanisms that will
        be used to solve the emergency response for fire-related emergencies in Lloret de Mar, Girona.
        \item \textbf{Teams Involved}:
            \begin{itemize}
                \item Emergency Services
                \item Firefighters
                \item Medical Services
                \item Public Communications
                \item \textit{Forensics}
            \end{itemize}
        \item \textbf{Overview}:
            \begin{itemize}
                \item For each crew: process definition and Pydantic outputs. 
                \item Agent interactions: flows and routers.
            \end{itemize}
    \end{itemize}
\end{frame}

\input{1-emergency-services}
\input{2-firefighters}
\input{3-medical-services}
\input{4-public-communications}
\input{5-crew-interaction}

\section{Conclusion}
\begin{frame}{Conclusion}
    \begin{itemize}
        \item \textbf{Emergency Services} establishes robust initial assessment and crew dispatching
        \item \textbf{Firefighters and Medical Services} demonstrates effective parallel operation and complex processes
        \item \textbf{Public Communications} generates useful summaries with mayor approval system and retry mechanisms
        \item We use a \textbf{centralized state management} with the CrewAI flow framework, enabling coordination between crews
        \item We use a \textbf{standardized reporting system} with structured outputs from each specialized crew, which will be compiled into a single report
    \end{itemize}
\end{frame}

\begin{frame}
    \centering
    \vspace{2cm}
    {\Large Thank You!}
    \vspace{1cm}
    
    {\large Questions?}
\end{frame}

% References
\begin{frame}{References}
    \begin{itemize}
        \item Wooldridge, Michael. An Introduction to MultiAgent Systems. 2nd ed., John Wiley \& Sons, 2009. ISBN 978-0-470-51946-2.
        \item Wooldridge, Michael. "Properties of Intelligent Autonomous Agents." YouTube, 26 Feb. 2010, \url{https://www.youtube.com/watch?v=vID-_uIfAvg}.
    \end{itemize}
\end{frame}

\end{document}
