\subsection{Firefighters}
This agent crew is responsible to move to the location of a fire and to extinguish the fire.
\newline The agents that are part of this crew are: a \textbf{fire chief}, one \textbf{equipment technician} and a team of \textbf{fire combatants}.

\subsubsection{Fire Chief}
Takes calls from the emergency services and reports back.

\begin{itemize}
    \item \textbf{Main task:} The fire chief receives a call from the emergency service operator and relays the information to its agent crew members. Once the firefighter crew arrives at the fire scene, the fire chief provides updates on the situation back to the emergency service operator.
    \item \textbf{Tools:}
    \begin{itemize}
        \item \textit{Communication Device}: A device for effective communication with the other crews.
    \end{itemize}
    \item \textbf{Type:} Facilitator agent.
    \item \textbf{Most relevant properties:}
    \begin{itemize}
        \item \textit{Flexibility:} The fire chief must be able to adapt to changing circumstances and new information, ensuring that the crew can respond effectively to dynamic situations on the fire scene.
        \item \textit{Reactivity:} The fire chief needs to respond promptly to incoming information and evolving conditions during emergencies, ensuring that the crew is informed and can adjust their actions accordingly.
        \item \textit{Social Ability:} Effective communication and collaboration with both the emergency service operator and other crews are crucial for the fire chief to facilitate coordination and ensure that all parties are updated on the situation.
    \end{itemize}
\end{itemize}

\subsubsection{Equipment Technician}
Manages material required to extinguish a fire.

\begin{itemize}
    \item \textbf{Main task:}  Based on the information received from the fire chief, the equipment technician needs to determine which materials are necessary, such as fire hoses, personal protective equipment (PPE), and fire extinguishers, and packs these items and loads them on the fire truck before the agent crew moves to the location of the fire. It is crucial that sufficient materials are packed to ensure a safe and effective response.
    \item \textbf{Tools:}
    \begin{itemize}
        \item \textit{Material Management Software}: Has a database of all the available material, which can be modified when resources are used for the emergencies.
    \end{itemize}
    \item \textbf{Type:} Information agent.
    \item \textbf{Most relevant properties:}
    \begin{itemize}
        \item \textit{Flexibility:} The agent must adapt to different emergency scenarios and equipment needs quickly.
        \item \textit{Reactivity:} The technician must respond promptly to changing conditions and requirements during firefighting operations.
        \item \textit{Rationality:} The agent needs to make logical decisions about what materials to prioritize and pack based on available information.
    \end{itemize}
\end{itemize}

\subsubsection{Firefighter}
Extinguishes the fire.

\begin{itemize}
    \item \textbf{Main task:} The firefighting combatants unload the required equipment from the fire truck at the fire scene. They then assess the most effective strategy to extinguish the fire by coordinating with their fellow firefighters.
    \item \textbf{Tools:}
    \begin{itemize}
        \item \textit{GPS}: Can access a real-time map of the city to locate the location of the incident and calculate the best route to get there.
    \end{itemize}
    \item \textbf{Type:} Collaborative agent.
    \item \textbf{Most relevant properties:}
    \begin{itemize}
        \item \textit{Reactivity:} This property is crucial as firefighting involves rapidly changing situations that require immediate responses to new developments, such as flare-ups or structural shifts.
        \item \textit{Proactiveness:} The combatant must anticipate potential challenges and take initiative in strategizing the best approach to extinguishing the fire, helping to prevent escalation and ensure successful outcomes.
        \item \textit{Social Ability:} Strong social ability is essential for effective teamwork, enabling the combatant to communicate and collaborate with fellow firefighters to coordinate efforts and ensure safety.
    \end{itemize}
\end{itemize}
