\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[top=1in, bottom=1in, left=1in, right=0.75in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{enumerate} % Import the enumerate package
\usepackage{amsfonts}
\usepackage{hyperref}
\usepackage{float}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{verbatim}


% Listings settings for Python code
\lstset{
    language=Python,
    basicstyle=\ttfamily\small,
    keywordstyle=\color{blue}\bfseries,
    stringstyle=\color{red},
    commentstyle=\color{green!70!black},
    numberstyle=\tiny\color{gray},
    numbers=left,
    stepnumber=1,
    numbersep=8pt,
    showspaces=false,
    showstringspaces=false,
    frame=single,
    breaklines=true,
    breakatwhitespace=true,
    tabsize=4,
    captionpos=b
}

\title{Emergency Response: Cooperation and Coordination Mechanisms in Multi-Agent Systems}
\author{Sheena Maria Lang, Antonio Lobo Santos, Zachary Parent, \\ María del Carmen Ramírez Trujillo and Bruno Sánchez Gómez}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Introduction}
In this report, we propose a robust framework to address the emergency response problem using cooperation and coordination
 mechanisms in multi-agent systems (MAS). The system, dubbed CrewAI, orchestrates diverse specialized crews to handle emergencies
  through structured processes, ensuring efficiency, precision, and adaptability. The approach integrates process definition, 
  pydantic outputs, and agent interaction, enabling smooth task execution and seamless inter-crew communication.
\\

The \textbf{process definition} outlines the workflows for individual crews, specifying sequential and parallel dependencies, agent roles,
 and key operational details. Each crew is equipped with tailored processes to ensure timely and effective responses.
\\ 

\textbf{Pydantic outputs} ensure consistency and clarity by defining structured data models for task outputs. These models are
 pivotal in facilitating inter-crew interactions and ensuring data integrity throughout the emergency response lifecycle.
\\ 

Finally, the \textbf{agent interaction} mechanism employs flow-based coordination, leveraging CrewAI’s advanced routing and state 
management capabilities. Through logical operators and conditional triggers, the framework ensures synchronization across crews, 
optimizing both task allocation and response accuracy.
\\ 

This comprehensive report details each component of the framework, emphasizing its adaptability and potential scalability. 
It serves as a blueprint for integrating multi-agent coordination into real-world emergency management systems.
\\

In the previous design process, we outlined the role of a \textbf{Forensics Team}, tasked with investigating the origins and causes 
of fires. This team included a \textit{Forensics Operator}, who facilitated communication and updates with other emergency crews, 
and a \textit{Forensics Coordinator}, responsible for managing team resources, assigning cases, and maintaining a database of current 
and historical incidents. The \textit{Coroner} performed examinations of bodies at fire scenes and conducted detailed analyses in the 
morgue, while the \textit{Investigator} handled on-site evidence collection, witness interviews, and cause determination. However, the 
primary objective of this work was to develop a framework for emergency response planning rather than diving deeply into specific 
scenarios or active interventions. As the forensic team’s functions extend beyond the immediate scope of emergency planning, it 
has been excluded in order to maintain the focus on the core objectives.


\input{sections/process_definition}


\input{sections/pydantic_output}


\input{sections/crew_interaction}


\section{Conclusion}
This report outlines the proposed cooperation and coordination mechanisms for the CrewAI MAS. Future work includes extending the interaction model to include additional agent types and testing the scalability of the system.


\end{document}
